% Eric Charles Grasby - Resume

% Last Revision Date: 2020-04-26

%%%% ============== BEGIN PREAMBLE ================== %%%%
\documentclass[11pt]{article}

% package imports
\usepackage{textcase}
\usepackage{anyfontsize}
\usepackage{enumitem}
\usepackage{wasysym}
\usepackage{relsize}
\usepackage{titlesec}
\usepackage[margin=0.5in]{geometry}

\titlespacing*{\section}{0pt}{2ex}{0ex}
\titlespacing*{\subsection}{0pt}{0ex}{-0.5ex}
\titlespacing*{\subsubsection}{0pt}{0ex}{-0.5ex}

\newcommand{\ualr}{University of Arkansas at Little Rock}
\newcommand{\uppr}[3]{ \noindent\MakeUppercase{{\fontsize{#2}{#3} \selectfont {#1}}} }
\author{Eric Charles Grasby}

%%%% ============== END PREAMBLE ================== %%%%

\begin{document}
\pagenumbering{gobble}
\begin{center}
\uppr{\textbf{Eric Charles Grasby}}{24}{28}
\vfill
Little Rock, AR \hfill \textbf{email} ecgrasby@ualr.edu \hfill \textbf{web} https://echarlesgrasby.xyz
\noindent \rule{1.0\textwidth}{0.4pt}
\end{center}

\section*{\uppr{Education}{14}{16}} \noindent \rule{1.0\textwidth}{0.4pt}
\textbf{Masters of Science, Information Quality} \hfill \textit{August 2017 - May 2020} \\
\ualr \\ \\
\textbf{Bachelors of Science, Information Science} \hfill \textit{August 2014 - May 2018} \\
\ualr

\section*{\uppr{Work Experience}{14}{16}} \noindent \rule{1.0\textwidth}{0.4pt}
\subsection*{Programmer/Analyst - IT Applications, Reliability}
Southwest Power Pool. Little Rock, AR \hfill \textit{May 2020 - Present} \\
\begin{itemize}
	\item Southwest Power Pool is a Regional Transmission Organization (RTO) that manages the bulk electric grid for utility and transmission companies across 14 US States.
\end{itemize}

FORTHCOMING
\\

\subsection*{Database Developer - Analyst}
Merkle Incorporated. Little Rock, AR \hfill \textit{May 2018 - May 2020} \\
\begin{itemize}
\item Merkle is a data-driven, tech-enabled marketing agency that, as of 2020, has over 10,000 employees
 \begin{itemize}
   \item Work on a development team that maintains both a large foundational marketing platform and a SOAP-based web service solution for a Fortune 500 financial company. As a developer, I often directly interface with client-side partners.
   \item Developed a tracking mechanism for a legacy campaign process that interfaced directly with our client's staff analysts.
   \item Used Powershell to develop adhoc scripts for process monitoring that were distributed to multiple teams at Merkle.
   \item Designed and wrote a custom monitoring script in Powershell to help ensure up-time of a web service solution that required availability 18 hours a day, seven days a week.
   \item Co-developed, with our team's tech lead, a data warehousing process in SQL Server to consolidate and match 500+ million back-logged records with a Merkle product database. This process has since been running on a weekly basis.
 \end{itemize}
\end{itemize}

\subsection*{Database Developer - Intern}
Merkle Incorporated. Little Rock, AR \hfill \textit{June 2017 - May 2018} \\
\begin{itemize}
 \item Migrated a shared library of bash and ksh scripts, used for campaign fulfillment, as part of a parallel server migration. Additionally, I isolated them into development and production environments.
 \item Implemented new weekly data feeds (approximately 200K records) into our solution's campaign selection warehouse
 \item Worked on a project to retire and update fields across a campaign fulfillment process. This involved scripting changes to 25+ different SQL Server database tables, stored procedures, and SSIS packages.
\end{itemize}

\subsection*{Due Diligence Analyst - Intern}
Fund For Arkansas' Future II, LLC (FAFII). Little Rock, AR \hfill \textit{September 2015 - December 2017} \\
\begin{itemize}
\item FAFII was an angel investment fund that infused seed capital into technology-based Arkansas startup companies. At the time, by capital assets, FAFII was the largest angel investment group in Arkansas.
 \begin{itemize}
  \item Authored comprehensive due diligence and market analysis reports on prospect companies.
  \item Took notes on company investment pitches and used those notes to help form questions for due diligence research.
  \item Worked directly with the Executive Director and Investment Committee to conduct follow-up interviews with startup company representatives (often the C-suite team) and industry experts.
  \item Maintained mission critical documentation for the fund, such as the Yearly Investor Report.
 \end{itemize}
\end{itemize}

\subsection*{Machine Operator}
Delta Well Screen Company, Incorporated. Jacksonville, AR \hfill \textit{Seasonal Position (Summers 2012-2016)} \\

\section*{\uppr{Technical Strengths}{14}{16}} \noindent\rule{1.0\textwidth}{0.4pt}
%%%% ============ BEGIN TECHNICAL SKILLS ========================= %%%%
\setlength{\leftmargini}{0pt}
\begin{enumerate}[topsep=0pt, partopsep=0pt, label=\null]

\item \textbf{Database Development}
  \begin{enumerate}[topsep=0pt, partopsep=0pt, label=\null]
  \item SQL, MS SQL Server, SQL Server Integration Services (SSIS), SAS DataFlux Data Management Studio
  \end{enumerate}
\item \textbf{Scripting Languages}
  \begin{enumerate}[topsep=0pt, partopsep=0pt, label=\null]
  \item Powershell (v2, v5), bash/sh/ksh, Python 3.x, awk
  \end{enumerate}
\item \textbf{Object-Oriented Languages}
  \begin{enumerate}[topsep=0pt, partopsep=0pt, label=\null]
  \item C\# \textit{(some experience)}, Java \textit{(academic experience)}
  \end{enumerate}
\item \textbf{Markup Languages}
  \begin{enumerate}[topsep=0pt, partopsep=0pt, label=\null]
  \item HTML5, CSS3, Markdown, {\LaTeX}
  \end{enumerate}
\item \textbf{Operating Systems}
  \begin{enumerate}[topsep=0pt, partopsep=0pt, label=\null]
  \item MS Windows 10, Windows Server 2016, Linux (RHEL, Ubuntu)
  \end{enumerate}
\item \textbf{Code Management}
  \begin{enumerate}[topsep=0pt, partopsep=0pt, label=\null]
  \item SVN/TortoiseSVN, WinMerge, Atlassian JIRA
  \end{enumerate}
\item \textbf{Documentation}
  \begin{enumerate}[topsep=0pt, partopsep=0pt, label=\null]
  \item MS Word, MS Excel, MS Visio, Atlassian Confluence, Adobe RoboHelp
  \end{enumerate}
\item \textbf{General Tooling}
  \begin{enumerate}[topsep=0pt, partopsep=0pt, label=\null]
  \item PuTTY, WinSCP, Vim, Notepad++, VS Code, Postman, Tableau, Linux coreutils (cp, find, gzip, grep, ssh, tar, etc.)
  \end{enumerate}

\end{enumerate}
%%%% ============  END TECHNICAL SKILLS ========================= %%%%

\section*{\uppr{Projects}{14}{16}}\noindent \rule{1.0\textwidth}{0.4pt}
(github) https://github.com/echarlesgrasby - My public github repositories \\
(this r\`esum\`e \textscale{1.5}{\smiley}) https://github.com/echarlesgrasby/mdcv - Written in {\LaTeX}
\section*{\uppr{Accolades}{14}{16}}\noindent \rule{1.0\textwidth}{0.4pt}
\setlength{\leftmargini}{0pt}
\begin{enumerate}[topsep=0pt, partopsep=0pt, label=\null]
\item Graduated Cum Laude. Masters of Science, \ualr \hfill \textit{May 2020}
\item Graduated Magna Cum Laude. Bachelors of Science, \ualr \hfill \textit{May 2018}
\item Eagle Scout. BSA Troop 770. Sherwood, Arkansas \hfill \textit{October 2009}
\end{enumerate}

\end{document}
